Uniform sampling without any cells to count trees

### 2024-07-01 Bootstrap.Rmd
Lundi soir

```{r}
install.packages("boot") # for bootstrap
library(readxl) # to read the initial file
library(data.table) # for shift
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

@@

```{r}
# Function to check if a point is inside a circle (indicator variable)
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(as.numeric(squared_distance <= R^2))
}
```

```{r}
circle <- function(x1, x2, R){
  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)

@@

```{r}
# Confidence Interval based on the percent approach
lim_inf <- est_boot[floor(B*2.5/100)]
lim_sup <- est_boot[B - floor(B*2.5/100)]
cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
```

@@

```{r}
res_boot <- boot(data=random_points, statistic=rho, R=10)
res_boot
```

>>>>

```{r}
install.packages("boot") # for bootstrap
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

@@

```{r}
# Function to check if a point is inside a circle (indicator variable)
source("~/work/Sim_article2024/Circle.R")

# Function to check if a point is inside a circle (indicator variable)
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(as.numeric(squared_distance <= R^2))
}
```

```{r}
circle <- function(x1, x2, R = 5){
  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)

@@

```{r}
# Confidence Interval based on the percentile approach
lim_inf <- est_boot[floor(B*2.5/100)]
lim_sup <- est_boot[B - floor(B*2.5/100)]
cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
```

```{r}
rho_init <- tibble(.rows = n)
# col_names <- c()
# for (c in 1:B) {
#   col_ <- paste("est", c, sep = "")
  # ech_ <- paste("ech", c, sep = "")
  # assign(ech_, df_boot[c])
  a <- c()
  for (i in 1:n) {
      a <- append(a, circle(random_points[i, 1], random_points[i, 2], R))
    }
  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
  # print(col_)
  rho_init <- rho_init %>% add_column("ech_init" = a) # 
  # col_names <- append(col_names, col_)
  # colnames(rho_boot) <- col_names
# }

# colnames(rho_boot) <- "ech_init"

# 3rd step: List of estimated totals thus obtained from each sample
est_init <- c()

est_tot <- sum((rho_init[1])/p)
est_init <- append(est_init, est_tot)

est_init <- sort(est_init)
```

```{r}
# Confidence Interval based on the reverse percentile approach
cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
```

@@

```{r}
res_boot <- boot(data=random_points, statistic=circle)
res_boot
# Doesn't work
```

### 2024-07-01 No_tree_no_grid.Rmd
Lundi soir

```{r}
library(readxl) # to read the initial file
library(data.table) # for shift
library(magrittr) # for pipes
library(tibble) # for add_column
```

@@

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
p
```

@@

@@

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

@@

```{r}
## The most simple function
fun1 <- function(x,y){
  1
}
```

```{r}
# 1 given to each sampled point
random_points$rho1 <- rep(1, n)
# Formula given in Cordy (1993), page 3
```

@@

```{r}
# Estimated value
est_area <- sum((random_points$rho1)/p) 
# Equal to 1e+06 whatever the chosen points
```

@@

```{r}
# Estimated value
est_ind <- sum((random_points$rho2)/p)
est_ind
# 510000 e.g.
```

@@

```{r}
# Estimated value
est_x <- sum((random_points$x)/p) # = 
est_x
# 499690876 e.g.
```

@@

Variance formula for the uniform case is based on the formula given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which gives a simplified formula for this particular case.

@@

```{r}
var_area <- est_carre/p - (1/n)*(est_area^2)
var_area
# The empirical variance is null as expected
```

```{r}
# fun1(x,y)^2 = fun1(x,y)
varTH_area <- area/p - (1/n)*(area^2)
varTH_area
# The theoretical variance is null as expected
# Since the total is equal to the area
```

@@

```{r}
var_ind <- est_ind/p - (1/n)*(est_ind^2)
var_ind
# Empirical variance: 2.491e+09 (huge)
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTH_ind <- half_area/p - (1/n)*(half_area^2)
varTH_ind
# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
# Close to the empirical one: great
```

@@

```{r}
# Estimated value
est_x2 <- sum(((random_points$x)^2)/p)
est_x2
# 499690876 e.g.
```

```{r}
var_x <- est_x2/p - (1/n)*(est_x^2)
var_x
# Empirical variance: 8.407871e+14 ?!
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
# varTH_x <- integral2(f_x, 0, 1000, 0, 1000)$Q/p - (1/n)*(integral2(f_x, 0, 1000, 0, 1000)$Q^2)
# varTH_x
# Theoretical variance: 2498391345, i.e. around 2.498e+09
# Close to the empirical one: great
```

@@

```{r}
# Making as many samples as necessary for MC (i.e. B)
for (b in 2:B) {
  x <- paste("x", b, sep = "")
  y <- paste("y", b, sep = "")
  # Uniform sampling over the whole territory
  a1 <- runif(n, 0, 1000)
  a2 <- runif(n, 0, 1000)
  # series_MC$x <- runif(n, 0, 1000)
  # series_MC$y <- runif(n, 0, 1000)
  # append()
  series_MC <- series_MC %>% add_column(x = a1, y = a2)
  col_names <- append(col_names, c(x, y))
}
colnames(series_MC) <- col_names
```

@@

@@

```{r}
# Empirical mean based on MC
mean(est_MC) # should be close to 5e+08
# 499121662 e.g.
```

```{r}
# Empirical standard deviation based on MC
sd(est_MC)
```

@@

true_vs_MC <- function(n, B, f, true_value){
  # n: sample size; B: number of iterations for MC; f: function to consider (with 2 variables, x and y)
  p <- sum(rep((1/1000)*(1/1000), n))

@@

  # 2nd step: creating the values corresponding to the function
  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  rho_MC$x.1 <- NULL
  rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_tot <- sum((rho_MC[c])/p)
    est_MC <- append(est_MC, est_tot)
  }

  est_value <- mean(est_MC) # Estimated value
  return(c(true_value, est_value))
}
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = fun1, true_value = 1e+06)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# 1e+06 1e+06 (Equality = great)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ind, true_value = 500000)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# True integral: 5e+05
# Mean of all the estimations: 499600
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_x, true_value = 5e+08)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])

#True integral: 5e+08
# Mean of all the estimations: 500189987
```

>>>>

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

@@

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
p
# p may be considered simply as a numeric
# since the inclusion density function is constant in this case
# Otherwise, we would need a vector
```

@@

We are looking for estimates of totals over the whole territory, i.e. double integrals of some functions.
To make such estimations, we begin with one single sample (made by uniform sampling).

@@

```{r}
# Dataframe to contain all coordinates of n randomly chosen points in a 1000x1000 square
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

@@

```{r}
## The most simple function
f_1 <- function(x,y){
  1
}
```

```{r}
# 1 given to each sampled point
random_points$rho1 <- rep(1, n)
```

@@

```{r}
# Estimated value
# Formula given in Cordy (1993), page 3
est_area <- sum((random_points$rho1)/p) 
# Equal to 1e+06 whatever the chosen points
```

```{r}
# Conclusion
cat("Total à estimer :", area, "\nEstimation :", est_area)
```

@@

```{r}
# Estimated value
est_ind <- sum((random_points$rho2)/p)
# 510000 e.g.
```

```{r}
# Conclusion
cat("Total à estimer :", half_area, "\nEstimation :", est_ind)
```

@@

```{r}
# Estimated value
est_x <- sum((random_points$x)/p)
# 499690876 e.g.
```

```{r}
# Conclusion
cat("Total à estimer :", val_x, "\nEstimation :", est_x)
```

@@

Variance formulas for the uniform case are based on the formulas given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which gives a simplified formula for this particular case.

@@

```{r}
var_area <- ((1000*1000)/(n-1))*est_carre - (1/(n-1))*(est_area^2)
# The empirical variance is null as expected
```

```{r}
# f_1(x,y)^2 = f_1(x,y)
varTHEO_area <- area/p - (1/n)*(area^2)
# The theoretical variance is null as expected
# Since the total is equal to the area
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_area, "\nVariance empirique :", var_area)
```

@@

```{r}
var_ind <- ((1000*1000)/(n-1))*est_ind - (1/(n-1))*(est_ind^2)
# Empirical variance: 2.491e+09 e.g.
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_ind <- half_area/p - (1/n)*(half_area^2)
# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
# Close to the empirical one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_ind, "\nVariance empirique :", var_ind)
```

@@

```{r}
# Value to estimate for this new function
val_x2 <- (10^12)/3
# Estimated value
est_x2 <- sum(((random_points$x)^2)/p)
# 499690876 e.g.
```

```{r}
var_x <- ((1000*1000)/(n-1))*est_x2 - (1/(n-1))*(est_x^2)
# Empirical variance: 8.407871e+14 ?!
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
# Close to the empirical one
```

```{r}
# Conclusion
cat("Variance théorique :", varTHEO_x, "\nVariance empirique :", var_x)
```

@@

```{r}
# Making as many samples as necessary for MC (i.e. B)
for (b in 2:B) {
  x <- paste("x", b, sep = "")
  y <- paste("y", b, sep = "")
  # Uniform sampling over the whole territory
  a1 <- runif(n, 0, 1000)
  a2 <- runif(n, 0, 1000)
  series_MC <- series_MC %>% add_column(x = a1, y = a2)
  col_names <- append(col_names, c(x, y))
}
colnames(series_MC) <- col_names
```

```{r}
rm(a1, a2, x, y, b, col_, col_names) # Useless now
```

@@

```{r}
rm(a, c, col_, col_names) # Useless now
```

@@

```{r}
rm(c, est_tot) # Useless now
```

```{r}
# Empirical mean based on MC
cat("Total à estimer :", val_x, "\nMoyenne des estimations obtenues :", mean(est_MC)) 
# should be close to 5e+08
# 499121662 e.g.
```

```{r}
# Empirical standard deviation based on MC
cat("Variance associée aux échantillons de Monte Carlo :", sd(est_MC))
# 28710306 e.g.
```

@@

true_vs_MC <- function(n, B, f){
  # n: sample size; B: number of iterations for MC; 
  # f: function to consider (with 2 variables, x and y)
  p <- sum(rep((1/1000)*(1/1000), n))

@@

  # 2nd step: creating the values corresponding to the function
  rho_MC <- tibble(.rows = n)
    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
    colnames(rho_MC) <- col_names
  }
  # rho_MC$x.1 <- NULL
  # rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_MC <- append(est_MC, sum((rho_MC[c])/p))
  }

  est_value <- mean(est_MC) # Estimated value
  return(est_value)
}
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
cat("True integral:", 1e+06, "\nMean of all the estimations:", res)
# 1e+06 1e+06 (Equality as always)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
cat("True integral:", 500000, "\nMean of all the estimations:", res)

# Ex:
# True integral: 5e+05
# Mean of all the estimations: 499600
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
cat("True integral:", 5e+08, "\nMean of all the estimations:", res)

# Ex:
# True integral: 5e+08
# Mean of all the estimations: 500189987
```

### 2024-07-01 Trees_no_grid.Rmd
Lundi soir

```{r}
install.packages("pracma") # double integral
install.packages("boot") # for bootstrap
library(readxl) # to read the initial file
library(data.table) # for shift
library(pracma)
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

@@

```{r}
# Sample size
n <- 100
```

```{r}
# Radius
R <- 5
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
```

@@

A sample is created by uniformly sampling the whole territory except the edge, which depends on the radius (to facilitate the calculation of the local variable).

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory except the edge
random_points$x <- runif(n, 0, 1000)
random_points$y <- runif(n, 0, 1000)
```

@@

```{r}
# New dataframe called trees_in (length = number of trees)
# Each column targets one point which was previously randomly chosen
# The value is 1 if the tree corresponding is inside the circle
trees_in <- data.frame(useless = rep(0,30942))
col_names <- c()
for (point in 1:n) {
  new_col <- paste("point", point, sep = "")
  a <- random_points[point,]$x
  b <- random_points[point,]$y
  val <- is_point_in_circle(a, b, trees$x, trees$y, R) #*point
  trees_in <- trees_in %>% add_column(new_col = val)
  col_names <- append(col_names, new_col)
}
trees_in[1] <- NULL
colnames(trees_in) <- col_names
```

@@

```{r}
# Creating a local variable (pages 10-11 in Trinh et alii (2024))
local_var <- c()
source("~/work/Sim_article2024/Inc_area.R")
for (placette in 1:n) {
  local_var <- append(local_var, sum(trees_in[trees_in[placette] != 0,]/inc_area(c(random_points[placette,]$x, random_points[placette,]$y),0,0,1000,1000,R)))
}

@@

  # 1st step: generating n samples
  series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
  col_names <- c("x1", "y1")
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    # Uniform sampling over the whole territory except the edge
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    series_MC <- series_MC %>% add_column(x = a1, y = a2)
    col_names <- append(col_names, c(x, y))
  }
  colnames(series_MC) <- col_names

  # 2nd step: creating the values corresponding to the function
  # Based on each sampled pair in all samples
  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- c()
    for (i in 1:n) {
      a <- append(a, circle(series_MC[i, (2*c)-1], series_MC[i, 2*c], R))
    }
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  rho_MC$x.1 <- NULL
  rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

>>>>

```{r}
install.packages("boot") # for bootstrap
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

@@

```{r}
# Sample size
n <- 100

# Radius
R <- 5

# Inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
```

@@

A sample is created by uniformly sampling the whole territory.

```{r}
# Dataframe containing all coordinates of n randomly chosen points
# Uniform sampling over the whole territory 
random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
```

@@

```{r}
# New dataframe called trees_in (length = number of trees)
# Each column targets one point which was previously randomly chosen
# The value is 1 if the tree corresponding is inside the circle
trees_in <- tibble(.rows = nrow(trees))
col_names <- c()
for (point in 1:n) {
  new_col <- paste("point", point, sep = "")
  a <- random_points[point,]$x
  b <- random_points[point,]$y
  val <- is_point_in_circle(a, b, trees$x, trees$y, R)
  trees_in <- trees_in %>% add_column(new_col = val)
  col_names <- append(col_names, new_col)
  colnames(trees_in) <- col_names
}
colnames(trees_in) <- col_names
```

@@

```{r}
# Creating a local variable (cf pages 10-11 in Trinh et alii (2024))
local_var <- c()
source("~/work/Sim_article2024/Inc_area.R")
for (placette in 1:n) {
  local_var <- append(local_var, sum(trees_in[trees_in[placette] != 0,]/inc_area(c(random_points[placette,]$x, random_points[placette,]$y),0,0,1000,1000,R)))
}

@@

  # 1st step: generating n samples
  series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
  col_names <- c("x1", "y1")
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    series_MC <- series_MC %>% add_column(x = a1, y = a2)
    col_names <- append(col_names, c(x, y))
  }
  colnames(series_MC) <- col_names

  # 2nd step: creating the values corresponding to the function
  # Based on each sampled pair in all samples
  rho_MC <- tibble(.rows = n)
    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- c()
    for (i in 1:n) {
      a <- append(a, circle(series_MC[i, (2*c)-1], series_MC[i, 2*c], R))
    }
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  # rho_MC$x.1 <- NULL
  # rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names
